### 2019-08-18 manuscript.Rmd
Modify for relative paths

---
bibliography: [/Users/mdozmorov/Documents/Work/VCU_grants/1_Dozmorov/networks.bib,/Users/mdozmorov/Documents/Work/VCU_grants/1_Dozmorov/brain.bib,/Users/mdozmorov/Documents/Work/VCU_grants/1_Dozmorov/enrichment.bib,/Users/mdozmorov/Documents/Work/VCU_grants/1_Dozmorov/3D_refs.bib]
csl: /Users/mdozmorov/Documents/Work/presentations/Templates/grant_template/styles.ref/genomebiology.csl
output:
  pdf_document: default
  word_document:
    reference_docx: /Users/mdozmorov/Documents/Work/presentations/Templates/manuscript_template/styles.doc/Arial_11_single_space_normal_margins.docx
  html_document: default
editor_options: 
  chunk_output_type: console
---

>>>>

---
bibliography: [refs/networks.bib,refs/brain.bib,refs/enrichment.bib,refs/3D_refs.bib]
csl: styles.ref/genomebiology.csl
output:
  pdf_document: default
  word_document:
    reference_docx: styles.doc/Arial_11_single_space_normal_margins.docx
  html_document: default
editor_options: 
  chunk_output_type: console
---
